---
title: "analysis"
author: "Jaden Orli"
date: "2023-03-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(RColorBrewer)
library(caret)
library(ggpubr)
library(MASS)
library(lme4)
library(kableExtra)
source("my_functions.R")
setup_libs()

display.brewer.all(colorblindFriendly = TRUE)
```


#1. Set up 

### a) Color Palette
```{r}
#choose a color palette
#display.brewer.pal(n = 8, name = 'OrRd')
#brewer.pal(n = 8, name = "OrRd")

#assign colors to names
adults = "#D7301F"
juveniles = "#FDBB84"
totals  = "#990000"
nico_eggs = "#FCC5C0"
crab_eggs = "#EF6548"
```


### b) Dataframes
```{r}
#read in the latest of the egg mortality data 
egg_mortality <- read_csv("NicothoidProjectAnalysis/RawData/eggmortalitydata.csv") %>% 
  clean_names() %>%
  select(!16:18) %>% 
  filter(!is.na(pleopod_number)) %>%
  filter(!eds == "M") %>%
  mutate(prop_viable_eggs = number_viable_crab_eggs/total_number_crab_eggs) %>% 
  mutate(prop_nonviable_eggs = total_number_non_viable_crab_eggs/total_number_crab_eggs) %>%
  mutate(total_nicos = (number_adult_nicos + number_juvenile_nicos)) 

#read in the egg mortality data that has development days
egg_mortality_day <- read_csv("NicothoidProjectAnalysis/RawData/eggmortality_day.csv") %>% 
  clean_names() %>%
  select(!17:19) %>% 
  filter(!is.na(pleopod_number)) %>%
  filter(!eds == "M") %>%
  mutate(prop_viable_eggs = number_viable_crab_eggs/total_number_crab_eggs) %>% 
  mutate(prop_nonviable_eggs = total_number_non_viable_crab_eggs/total_number_crab_eggs)

#read in the dissections data
dissections <- read_csv("NicothoidProjectAnalysis/RawData/all_dissections.csv") %>% 
  clean_names() %>%
  select(1:4, 9, 10) %>%
  filter(!is.na(nicothoid_count)) %>%
  filter(!nicothoid_count == "N/A") %>%
  filter(!number_of_lamellae == "NA") %>%
  mutate_at(c(5,6), as.numeric) %>%
  mutate(prop_nicos = nicothoid_count/number_of_lamellae)

autoinfection <- read_csv("NicothoidProjectAnalysis/RawData/first_broods_only.csv") %>% 
  clean_names() %>%
  select(!11) %>%
  select(!13:18) %>%
  filter(!experiment_id == "Autoinfection-055") %>%
  mutate_at(9, as.numeric) %>%
  filter(!total_number_of_eggs == 0)

```


# 2. Timeseries Visualization

### a) Egg Mortality Data by EDS 
```{r}
#visualize the change in proportion of viable eggs over time
#subset the data with the desireds columns
egg_mort_viable <- egg_mortality %>%
  select(4,16)


#plot the data for the longer dataframe with the averages as groups
eggs_mort_eds_vis <- ggplot(data = egg_mort_viable, 
       aes(x = eds, y = prop_viable_eggs)) +
  geom_point(color = crab_eggs) +
  theme_gray() +
  geom_smooth(method = lm, level = 0.95, color = "black") +
  ylab("Proportion Viable Crab Eggs") +
  xlab("Egg Development Stage (EDS)") + 
  ggtitle("Egg Mortality Across EDS") +
  theme(plot.title = element_text(hjust = 0.5))

#create a data frame with the average values across each EDS 
eggs_mort_eds_avg <- egg_mortality %>%
  group_by(eds) %>%
  summarize(avg_prop_viable_eggs = mean(prop_viable_eggs),
            avg_prop_nonviable_eggs = mean(prop_nonviable_eggs)) %>%
  as_tibble()


#plot the data for the dataframe with the averages as groups
eggs_mort_eds_avg_vis <- ggplot(data = eggs_mort_eds_avg, 
       aes(x = eds, y = avg_prop_viable_eggs)) +
  geom_point(color = crab_eggs) +
  theme_gray() +
  geom_smooth(method = lm, level = 0.95, color = "black") +
  ylab("Average Proportion Viable Crab Eggs") +
  xlab("Egg Development Stage (EDS)") + 
  ggtitle("Average Egg Mortality Across EDS") +
  theme(plot.title = element_text(hjust = 0.5))


#remove the most highly infested crabs (037, 043, and 045)
new_crab_eds <- egg_mortality %>%
  filter(!crab_id == "ANT-GAV-037") %>%
  filter(!crab_id == "ANT-GAV-045") %>%
  filter(!crab_id == "ANT-GAV-043")

#create a data frame with the average values across each day 
eggs_mort_avg_new_eds <- new_crab_eds %>%
  group_by(eds) %>%
  summarize(avg_prop_viable_eggs = mean(prop_viable_eggs),
            avg_prop_nonviable_eggs = mean(prop_nonviable_eggs)) %>%
  as_tibble()

#plot the data for the longer dataframe with the averages as groups
eggs_mort_vis_new_eds <- ggplot(data = eggs_mort_avg_new_eds, 
       aes(x = eds, y = avg_prop_viable_eggs)) +
  geom_point(color= crab_eggs) +
  theme_gray() +
  geom_smooth(method = lm, level = 0.95, color = "black") +
  ylab("Average Proportion Viable Crab Eggs") +
  xlab("Egg Development Stage (EDS)") + 
  ggtitle(label = "Average Egg Mortality Across EDS",
          subtitle = "Low Infestation Crabs") +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))

#plot the graphs
eggs_mort_eds_vis
eggs_mort_eds_avg_vis
eggs_mort_vis_new_eds

```


### b) Egg Mortality Data by Development Day

#### i) All the Crabs
```{r}
#create a data frame with the average values across each development day 
eggs_mort_day_avg <- egg_mortality_day %>%
  group_by(day) %>%
  summarize(avg_prop_viable_eggs = mean(prop_viable_eggs),
            avg_prop_nonviable_eggs = mean(prop_nonviable_eggs),
            avg_adult_nicos = mean(number_adult_nicos),
            avg_juvenile_nicos = mean(number_juvenile_nicos),
            avg_nico_eggs = mean(number_nico_eggs),
            crab_id = crab_id) %>%
  as_tibble()

#pivot the data longer 
eggs_mort_day_long <- eggs_mort_day_avg %>%
  pivot_longer(names_to = "averages",
               cols = c("avg_prop_viable_eggs", "avg_prop_nonviable_eggs"))


#plot the data for the dataframe with the averages as groups
eggs_mort_day_vis_abline <- ggplot(data = eggs_mort_day_avg, 
       aes(x = day, y = avg_prop_viable_eggs)) +
  geom_point(color= crab_eggs) +
  theme_gray() +
  geom_smooth(method = lm, level = 0.95, color = "black") +
  ylab("Average Proportion Viable Crab Eggs") +
  xlab("Development Day") + 
  ggtitle("Egg Mortality Across Development Days") +
  theme(plot.title = element_text(hjust = 0.5))

#plot the graphs
eggs_mort_day_vis_abline

#plot the data for the dataframe with the averages as groups
eggs_mort_day_vis <- ggplot(data = eggs_mort_day_avg, 
       aes(x = day, y = avg_prop_viable_eggs)) +
  geom_point(color= crab_eggs) +
  theme_gray() +
  ylab("Average Proportion Viable Crab Eggs") +
  xlab("Development Day") + 
  ggtitle("Egg Mortality Across Development Days") +
  theme(plot.title = element_text(hjust = 0.5))

#plot the graphs
eggs_mort_day_vis

```


#### ii) Low Infestation Only
```{r}
#remove the most highly infested crabs (037, 043, and 045)
low_infested <- egg_mortality_day %>%
  filter(!crab_id == "ANT-GAV-037") %>%
  filter(!crab_id == "ANT-GAV-045") %>%
  filter(!crab_id == "ANT-GAV-043")

#create a data frame with the average values across each day 
eggs_mort_avg_low <- low_infested %>%
  group_by(day) %>%
  summarize(avg_prop_viable_eggs = mean(prop_viable_eggs),
            avg_prop_nonviable_eggs = mean(prop_nonviable_eggs)) %>%
  as_tibble()

#plot the data for the longer dataframe with the averages as groups with an abline
eggs_mort_vis_low_abline <- ggplot(data = eggs_mort_avg_low, 
       aes(x = day, y = avg_prop_viable_eggs)) +
  geom_point(color = crab_eggs) +
  theme_gray() +
  geom_smooth(method = lm, level = 0.95, color = "black") +
  ylab("Average Proportion Viable Crab Eggs") +
  xlab("Development Day") + 
  ggtitle(label = "Average Egg Mortality Across Development Day",
          subtitle = "Low Infestation Crabs") +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))

#plot the graph
eggs_mort_vis_low_abline

#plot the data for the longer dataframe with the averages as groups wihtout an abline
eggs_mort_vis_low <- ggplot(data = eggs_mort_avg_low, 
       aes(x = day, y = avg_prop_viable_eggs)) +
  geom_point(color = crab_eggs) +
  theme_gray() +
  ylab("Average Proportion Viable Crab Eggs") +
  xlab("Development Day") + 
  ggtitle(label = "Average Egg Mortality Across Development Day",
          subtitle = "Low Infestation Crabs") +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))

#plot the graph
eggs_mort_vis_low

```


#### iii) High Infestation Only
```{r}
#keep the most highly infested crabs (037, 043, and 045)
high_infested <- egg_mortality_day %>%
  filter(crab_id == "ANT-GAV-037" |crab_id == "ANT-GAV-045") 

#create a data frame with the average values across each day 
eggs_mort_avg_high <- high_infested %>%
  group_by(day) %>%
  summarize(avg_prop_viable_eggs = mean(prop_viable_eggs),
            avg_prop_nonviable_eggs = mean(prop_nonviable_eggs)) %>%
  as_tibble()

#plot the data for the longer dataframe with the averages as groups with an abline
eggs_mort_vis_high_abline <- ggplot(data = eggs_mort_avg_high, 
       aes(x = day, y = avg_prop_viable_eggs)) +
  geom_point(color = crab_eggs) +
  theme_gray() +
  geom_smooth(method = lm, level = 0.95, color = "black") +
  ylab("Average Proportion Viable Crab Eggs") +
  xlab("Development Day") + 
  ggtitle(label = "Average Egg Mortality Across Development Day",
          subtitle = "High Infestation Crabs") +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))

#plot the graph
eggs_mort_vis_high_abline

#plot the data for the longer dataframe with the averages as groups without an abline
eggs_mort_vis_high <- ggplot(data = eggs_mort_avg_high, 
       aes(x = day, y = avg_prop_viable_eggs)) +
  geom_point(color = crab_eggs) +
  theme_gray() +
  ylab("Average Proportion Viable Crab Eggs") +
  xlab("Development Day") + 
  ggtitle(label = "Average Egg Mortality Across Development Day",
          subtitle = "High Infestation Crabs") +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))

#plot the graph
eggs_mort_vis_high

```


# 3. Counts Visualization
```{r}
#plot the number of adult nicos against the total number of viable eggs
adult_plot <- ggplot(data = egg_mortality, 
       aes( y = prop_viable_eggs, x = number_adult_nicos)) +
  geom_point(color = adults) + 
  geom_smooth(method = lm, level = 0.95, color = "black") +
  theme_gray() +
  xlab("Counts") +
  ylab("Proportion of Viable Crab Eggs") + 
  ggtitle("Adult Nicos") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.title.y = element_text(size = 6),
        axis.title.x = element_text(size = ))

#plot the number of juvenile nicos against the total number of viable eggs 
juvenile_plot <- ggplot(data = egg_mortality, 
       aes(y = prop_viable_eggs, x = number_juvenile_nicos)) +
  geom_point(color = juveniles) + 
  geom_smooth(method = lm, level = 0.95, color = "black") +
  theme_gray() +
  xlab("Counts") +
  ylab("Proportion of Viable Crab Eggs") + 
  ggtitle("Juvenile Nicos") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.title.y = element_text(size = 6),
        axis.title.x = element_text(size = 7)) 

#plot the number of total number of nicos against the total number of viable eggs
total_plot <- ggplot(data = egg_mortality, 
       aes( y = prop_viable_eggs, x = total_nicos)) +
  geom_point(color = totals) + 
  geom_smooth(method = lm, level = 0.95, color = "black") +
  theme_gray() +
  xlab("Counts") +
  ylab("Proportion of Viable Crab Eggs") + 
  ggtitle("Total Nicos") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.title.y = element_text(size = 6),
        axis.title.x = element_text(size = 7))


#plot the number of nico eggs against the total number of viable eggs
nico_egg_plot <- ggplot(data = egg_mortality, 
       aes(y = prop_viable_eggs, x = number_nico_eggs)) +
  geom_point(color = nico_eggs) + 
  geom_smooth(method = lm, level = 0.95, color = "black") +
  theme_gray() +
  xlab("Counts") +
  ylab("Proportion of Viable Crab Eggs") + 
  ggtitle("Number Nico Eggs") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.title.y = element_text(size = 6),
        axis.title.x = element_text(size = 7)) 
  
#add the plots together
ggarrange(adult_plot, juvenile_plot, total_plot, nico_egg_plot,
                           labels = c("a)", "b)", "c)", "d)"),
                           ncol = 2, nrow = 2)



## we see that there is a clear relationship between the proportion of nonviable eggs and the number of nico eggs while there isn't always this clear relationship with the total number of nicos and the proportion of nonviable eggs
## this is why I want to do things in terms of biomass because the adult nicos are transforming the crab egg biomass directly into nico egg biomass
```

# 4. Visually Evaluate Normality
```{r}
#look at the frequency of the count data for all the life stages

#plot the frequency of adult nicos 
adult_plot_hist <- gghistogram(data = egg_mortality, 
                               x = "number_adult_nicos", 
                               fill = adults) +
  theme_gray() +
  ylab("Counts") +
  xlab("Frequency") + 
  ggtitle("Adult Nicos") +
  theme(plot.title = element_text(hjust = 0.5))

#plot the frequency of juvenile nicos 
juvenile_plot_hist <- gghistogram(data = egg_mortality, 
                               x = "number_juvenile_nicos",
                               fill = juveniles) +
  theme_gray() +
  ylab("Counts") +
  xlab("Frequency") + 
  ggtitle("Juvenile Nicos") +
  theme(plot.title = element_text(hjust = 0.5))

#plot the frequency of total nicos 
total_plot_hist <- gghistogram(data = egg_mortality, 
                               x = "total_nicos",
                               fill = totals) +
  theme_gray() +
  ylab("Counts") +
  xlab("Frequency") + 
  ggtitle("Total Nicos") +
  theme(plot.title = element_text(hjust = 0.5))


#plot the frequency of juvenile nicos 
nico_eggs_plot_hist <- gghistogram(data = egg_mortality, 
                               x = "number_nico_eggs",
                               fill = nico_eggs) +
  theme_gray() +
  ylab("Counts") +
  xlab("Frequency") + 
  ggtitle("Nicos Eggs") +
  theme(plot.title = element_text(hjust = 0.5))

#combine the plots 
ggarrange(adult_plot_hist, juvenile_plot_hist, total_plot_hist, nico_eggs_plot_hist,
                           labels = c("a)", "b)", "c)", "d)"),
                           ncol = 2, nrow = 2)

## it is obvious that the count data is heavily right skewed
```



# 5. Analysis (Egg Mass)

### a) Generalized Linear Models EDS
```{r}
#create a generalized linear model to evaluate the relationship between viable eggs and number of adult nicos

##poisson 
glm.adults.poisson <- glmer(number_viable_crab_eggs ~ number_adult_nicos + (1|crab_id), 
                   data = egg_mortality, 
                   family = "poisson")

##negative binomial 
glm.adults.nb <- glmer.nb(number_viable_crab_eggs ~ number_adult_nicos + (1|crab_id), 
                   data = egg_mortality)

#create a generalized linear model to evaluate the relationship between viable eggs and number of juvenile nicos

##poisson 
glm.juveniles.poisson <- glmer(number_viable_crab_eggs ~ number_juvenile_nicos + (1|crab_id), 
                   data = egg_mortality, 
                   family = "poisson")

##negative binomial 
glm.juveniles.nb <- glmer.nb(number_viable_crab_eggs ~ number_juvenile_nicos + (1|crab_id), 
                   data = egg_mortality)
 

#create a generalized linear model to evaluate the relationship between viable eggs and number of nicos eggs

##poisson 
glm.nicoeggs.poisson <- glmer(number_viable_crab_eggs ~ number_nico_eggs + (1|crab_id), 
                   data = egg_mortality, 
                   family = "poisson")

##negative binomial 
glm.nicoeggs.nb <- glmer.nb(number_viable_crab_eggs ~ number_nico_eggs + (1|crab_id), 
                   data = egg_mortality)

#evaluate with interactions of all of the states

##poisson 
#glm.combined.poisson <- glmer(number_viable_crab_eggs ~ number_adult_nicos*number_juvenile_nicos*number_nico_eggs + (1|crab_id), 
                   #data = egg_mortality, 
                   #family = "poisson")

##negative binomial 
#glm.combined.nb <- glmer.nb(number_viable_crab_eggs ~ number_adult_nicos*number_juvenile_nicos*number_nico_eggs + (1|crab_id), 
                   #data = egg_mortality)

```


### b) Generalized Linear Models Development Day
```{r}
glm.adults.poisson <- glmer(number_viable_crab_eggs ~ number_adult_nicos + (1|eds), 
                   data = egg_mortality_day, 
                   family = "poisson")
```




### c) Mean Density
```{r}
#create a data frame with the scaled density of the adults in the egg mass per 1000 eggs
egg_mortality_density <- egg_mortality %>%
  mutate(density_adult_nicos = ((number_adult_nicos/total_number_crab_eggs)*1000)) %>%
  mutate(density_juvenile_nicos = ((number_juvenile_nicos/total_number_crab_eggs)*1000)) %>%
  mutate(density_total_nicos = ((total_nicos/total_number_crab_eggs)*1000)) %>%
  mutate(density_nico_eggs = ((number_nico_eggs/total_number_crab_eggs)*1000))

#calculate the mean density of each of the values 
mean_adult_density <- mean(egg_mortality_density$density_adult_nicos)
mean_adult_density

mean_juvenile_density <- mean(egg_mortality_density$density_juvenile_nicos)
mean_juvenile_density

mean_total_density <- mean(egg_mortality_density$density_total_nicos)
mean_total_density

mean_nico_egg_density <- mean(egg_mortality_density$density_nico_eggs)
mean_nico_egg_density

```
### d) Mean Density (adults with all data)
```{r}
#create a column in the autoinfection data with the density of adult nicos
autoinfection_density <- autoinfection %>%
  mutate(density_adult_nicos = ((number_of_adult_copepods/total_number_of_eggs)*1000)) %>%
  select(1,9,13) %>%
  rename(number_adult_nicos = number_of_adult_copepods)

#subset the egg morality data for just the adults and the adult density
mort_egg_density <- egg_mortality_density %>%
  select(1,11,19)

#join the two dataframes for the adult density
mort_egg_density_combined <- rbind(mort_egg_density, autoinfection_density)

#calculate the mean density of the adults
mean_adult_density_all <- mean(mort_egg_density_combined$density_adult_nicos)
mean_adult_density_all

```


### e) Mean Intensity (ignore)
```{r}
#calculate the mean intensity of each of the values 
mean_adult_intensity <- mean(egg_mortality$number_adult_nicos)
mean_adult_intensity
# we need to eventually find a way to scale this up to the whole crab ΟTHERWISE ITS NOT INTENSITY - 700 thousand to 3.3 millon eggs 

mean_juvenile_intensity <- mean(egg_mortality$number_juvenile_nicos)
mean_juvenile_intensity

mean_total_intensity <- mean(egg_mortality$total_nicos)
mean_total_intensity

mean_nico_egg_intensity <- mean(egg_mortality$number_nico_eggs)
mean_nico_egg_intensity
```

### f) Mean Egg Mortality
```{r}
#look at the summary stats
summary_egg_mortality <- summary(egg_mortality$prop_nonviable_eggs)
summary_egg_mortality

#calculate the mean egg mortality as a percent
mean_egg_mortality <- mean((egg_mortality$prop_nonviable_eggs)*100)
mean_egg_mortality

#calculate the min egg mortality as a percent
min_egg_mortality <- min((egg_mortality$prop_nonviable_eggs)*100)
min_egg_mortality

#calculate the max egg morality as a percent
max_egg_mortality <- max((egg_mortality$prop_nonviable_eggs)*100)
max_egg_mortality
```

# 6. Analysis (Gills)

### a) Mean Density 

#### i) All Species/All Sexes
```{r}
#create a data frame with the density of juvenile nicos per lamellae 
gill_density <- dissections %>%
  mutate(density_nicos_gills = (nicothoid_count/number_of_lamellae)) 

#calculate the mean density of the nicos in the gills
mean_density_gills <- mean(gill_density$density_nicos_gills)
mean_density_gills

```

#### ii) All Sexes Yellow Crabs
```{r}
#subset for yellows only

##sample size n = 21
yellow_all <- gill_density %>%
  filter(!crab_id %in% c("PRO-GAV-001", "PAG-GAV-001", "MPRO-GAV-002")) 

yellow_all_mean_density <- mean(yellow_all$density_nicos_gills)
yellow_all_mean_density

```


#### iii) All Sexes Red Crabs 
```{r}
#subset for reds only

##sample size n = 2
red_all <- gill_density %>%
  filter(crab_id %in% c("PRO-GAV-001","MPRO-GAV-002")) 

red_all_mean_density <- mean(red_all$density_nicos_gills)
red_all_mean_density

```


#### iv) All Sexes Brown Crabs
```{r}
#subset for browns only

##sample size n = 1
brown_all <- gill_density %>%
  filter(crab_id %in% c("PAG-GAV-001")) 

brown_all_mean_density <- mean(brown_all$density_nicos_gills)
brown_all_mean_density

```


#### v) All Species Males
```{r}
#subset for all males

##sample size n = 7
males_all <- gill_density %>%
  filter(crab_id %in% c("MANT-GAV-001","MANT-GAV-002", "MANT-GAV-008", "MANT-GAV-009", "MANT-GAV-010", "MANT-GAV-011", "MPRO-GAV-002")) 

males_all_mean_density <- mean(males_all$density_nicos_gills)
males_all_mean_density

```


#### vi) All Species Females
```{r}
#subset for all females

##sample size n = 20
females_all <- gill_density %>%
  filter(!crab_id %in% c("MANT-GAV-001","MANT-GAV-002", "MANT-GAV-008", "MANT-GAV-009", "MANT-GAV-010", "MANT-GAV-011", "MPRO-GAV-002")) 

females_all_mean_density <- mean(females_all$density_nicos_gills)
females_all_mean_density
```


### b) Mean Intensity (ignore)
```{r}
#divide the nicos/lamallae*the number of gills (12 gills per crab)
gill_intensity <- gill_density %>%
  mutate(intensity_nicos_gills = (density_nicos_gills*12))

#calculate the mean intensity for the nicos in the gills 
mean_intensity_gills <- mean(gill_intensity$intensity_nicos_gills)
mean_intensity_gills

```


### c) Mean Density 

#### i) Yellow Males
```{r}
#subset for yellow males only
##I chose to exclude two males we dissected because they had been held for over a month before dissection and I believe that this is why they didn't have nicos -- we are planning to do a few more male dissections

##sample size n = 6
yellow_males <- gill_density %>%
  filter(crab_id %in% c("MANT-GAV-001","MANT-GAV-002", "MANT-GAV-008", "MANT-GAV-009", "MANT-GAV-010", "MANT-GAV-011")) 

yellow_males_mean_density <- mean(yellow_males$density_nicos_gills)
yellow_males_mean_density

```

#### ii) Red Males
```{r}
#subset for red males only
##I chose to exclude two males we dissected because they had been held for over a month before dissection and I believe that this is why they didn't have nicos -- we are planning to do a few more male dissections

##sample size n = 1
red_males <- gill_density %>%
  filter(crab_id == "MPRO-GAV-002") 

red_males_mean_density <- mean(red_males$density_nicos_gills)
red_males_mean_density
```

#### iii) Brown Males
```{r}

```


### d) Mean Density 

#### i) Yellow Females
```{r}
#subset for yellow females only

##sample size n = 16
yellow_females <- gill_density %>%
  filter(!crab_id %in% c("MANT-GAV-001","MANT-GAV-002", "MANT-GAV-003", "MANT-GAV-005", "PRO-GAV-001", "PAG-GAV-001", "MANT-GAV-008", "MANT-GAV-009", "MANT-GAV-010", "MANT-GAV-011", "MPRO-GAV-002")) 

yellow_females_mean_density <- mean(yellow_females$density_nicos_gills)
yellow_females_mean_density

```


#### ii) Red Females
```{r}
#subset for red females only

##sample size n = 1
red_females <- gill_density %>%
  filter(crab_id == "PRO-GAV-001") 

red_females_mean_density <- mean(red_females$density_nicos_gills)
red_females_mean_density

```


#### iii) Brown Females
```{r}
#subset for brown females only

##sample size n = 1
brown_females <- gill_density %>%
  filter(crab_id == "PAG-GAV-001") 

brown_females_mean_density <- mean(brown_females$density_nicos_gills)
brown_females_mean_density

```



### e) Mean Intensity (Yellow Males) (ignore)
```{r}
#calculate the mean intensity for the nicos in the gills 
male_mean_intensity_gills <- mean(males$intensity_nicos_gills)
male_mean_intensity_gills

```


### f) Mean Intensity (Yellow Females) (ignore)
```{r}
#calculate the mean intensity for the nicos in the gills 
female_mean_intensity_gills <- mean(females$intensity_nicos_gills)
female_mean_intensity_gills

```

# 7. Table with Density

#### a) Create a Table 
```{r}
#create a string with all the data 
data_yellow <- c(NA, NA, yellow_males_mean_density, NA, mean_nico_egg_density, mean_juvenile_density, yellow_females_mean_density, mean_adult_density_all)

#turn the string into a matrix
matrix_yellow <- matrix(data_yellow, ncol = 4, byrow = TRUE)
colnames(matrix_yellow) <- c("Nicothoid Eggs", "Juvenile Nicothoids in Egg Mass", "Juvenile Nicothoids in Gills", "Adult Nicothoids in Egg Mass")
rownames(matrix_yellow) <- c("Male C. anthonyi", "Female C. anthonyi")

#create the table
table_yellow <- matrix_yellow %>%
  kbl(caption = "<center>Density of Nicothoids</center>", html_font = "Times New Roman") %>%
  kable_classic(full_width = F, html_font = "Times New Roman") %>%
  row_spec(row = 1, italic = TRUE) %>%
  row_spec(row = 2, italic = TRUE) %>%
  kable_styling(font_size = 8) %>%
  footnote(symbol = "The density of the nicothoids in the egg mass are calculated per one thousand crab eggs.")

table_yellow
```

